---
title: "Using `RTCGA` package to download mRNA data that are included in RTCGA.mRNA.20160128 package" 
subtitle: "Date of datasets release: 2016-01-28 "
author: " Marcin Kosinski <m.p.kosinski@gmail.com> "
date: " 2016-12-30 "
output: rmarkdown::html_vignette 
vignette: > 
  %\VignetteIndexEntry{Using RTCGA package to download mRNA data that are included in RTCGA.mRNA.20160128 package"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo=FALSE}
library(knitr)
opts_chunk$set(
	comment = "",
	message = FALSE,
	warning = FALSE,
	tidy.opts = list(
		keep.blank.line = TRUE,
		width.cutoff= 150),
	options(width= 150),
	eval = FALSE
)
```
# RTCGA.mRNA.20160128 

This package was created with [`RTCGA::createTCGA()`](http://rtcga.github.io/RTCGA/staticdocs/createTCGA.html) function and is a part of [RTCGA](http://rtcga.github.io/RTCGA/) project. It consist of
data from [The Cancer Genome Atlas Project](https://cancergenome.nih.gov/abouttcga). 

Datasets existing in this package were downloaded automatically from [Firehose Broad GDAC](http://gdac.broadinstitute.org/) portal. They were taken
from the 2016-01-28 release date. All release dates are available [here](http://gdac.broadinstitute.org/runs/). Datasets were downloaded with the use of `RTCGA::downloadTCGA()` function and were transposed with `RTCGA::readTCGA()` function.

The package contains following datasets, which names corresponds to: the cohort type, data type and release date. Cohort types can be checked
with `RTCGA::infoTCGA()`, release dates with `RTCGA::checkTCGA('Dates')` and data types with e.g. `RTCGA::checkTCGA('DataSets', 'BRCA')` calls. 
The used data type for this package was ` agilentg4502a_07_3__unc_edu__Level_3 ` - all those information are included in the `DESCRIPTION` file. To see
the manual page for included datasets run  `?mRNA.20160128` in R console. 

-  BRCA.mRNA.20160128 - class: data.frame - nrow: 590 - ncol: 17815 
-  COADREAD.mRNA.20160128 - class: data.frame - nrow: 244 - ncol: 17815 
-  GBMLGG.mRNA.20160128 - class: data.frame - nrow: 27 - ncol: 17815 
-  GBM.mRNA.20160128 - class: data.frame - nrow: 27 - ncol: 17815 
-  KIPAN.mRNA.20160128 - class: data.frame - nrow: 88 - ncol: 17815 
-  KIRC.mRNA.20160128 - class: data.frame - nrow: 72 - ncol: 17815 
-  KIRP.mRNA.20160128 - class: data.frame - nrow: 16 - ncol: 17815 
-  LUAD.mRNA.20160128 - class: data.frame - nrow: 32 - ncol: 17815 
-  LUSC.mRNA.20160128 - class: data.frame - nrow: 154 - ncol: 17815 
-  OV.mRNA.20160128 - class: data.frame - nrow: 561 - ncol: 17815 
-  UCEC.mRNA.20160128 - class: data.frame - nrow: 54 - ncol: 17815 

Optionally, the data can be loaded through the [ExperimentHub](http://www.bioconductor.org/packages/3.4/bioc/vignettes/ExperimentHubData/inst/doc/ExperimentHubData.html) interface.

```{r, eval=FALSE}
library(ExperimentHub)
eh <- ExperimentHub()
myfiles <- query(eh,  "RTCGA.mRNA.20160128" )
myfiles[[1]]  ## load the first resource in the list
```


# Notes

Note that this package is a data package with datasets from 2016-01-28 release date. There are few data packages already on Bioconductor with datasets from "2015-11-01". To read more check `?RTCGA::datasetsTCGA`.